A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-18 writeup/paper.tex
Added markers to show affliations.

@@

\author{Ellie Pavlick \ \ \ \ \ \ \ \ \ \ Dmitry Kachaev \ \ \ \ \ \ \ \ \ \  Chris Callison-Burch \\
Computer and Information Science Department, University of Pennsylvania \\
Human Language Technology Center of Excellence, Johns Hopkins University \\
  }

>>>>

\newcommand{\affliationPenn}{\ensuremath{{}^\text{1}}}
\newcommand{\affliationJHU}{\ensuremath{{}^\text{2}}}

@@

\author{Ellie Pavlick\affliationPenn \ \ \ \ \ \ \ \ \ \ Dmitry Kachaev\affliationJHU \ \ \ \ \ \ \ \ \ \  Chris Callison-Burch\affliationPenn$^{,}$\affliationJHU \\
\affliationPenn Computer and Information Science Department, University of Pennsylvania \\
\affliationJHU Human Language Technology Center of Excellence, Johns Hopkins University \\
  }
